%-------------------------
% Entry-level Cover-letter Template in LaTeX
% Made to go with "Entry-level Resume in laTeX" - here
% Version - v1.0
% Last Edits - October 5, 2021
% Author : Jayesh Sanwal
% Reach out to me on LinkedIn(/in/jsanwal), with any suggestions, ideas, issues, etc.
%------------------------
% !TEX program = xelatex


%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  STARTING HERE, DO NOT TOUCH ANYTHING 
%%%%%%% --------------------------------------------------------------------------------------

%%%% Define Document type
\documentclass[11pt,a4]{article}

%%%% Include Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
 \usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{ragged2e}
\usepackage{anyfontsize}

%%%% Set Margins
\usepackage[margin=1cm]{geometry}

%%%% Set Fonts
\setmainfont[
BoldFont=SourceSansPro-Semibold.otf,
ItalicFont=SourceSansPro-RegularIt.otf
]{SourceSansPro-Regular.otf}

%%%% Set Page Style
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color, Page Number Color, Footer Text
\definecolor{UI_blue}{RGB}{32, 64, 151}
\definecolor{HF_color}{RGB}{179, 179, 179}

%%%% Set Heading Format
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-0.7cm} \hrulefill \vspace{-0.2cm}]
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  END OF "DO NOT TOUCH" REGION
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------



\begin{document}
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  HEADER
%%%%%%% --------------------------------------------------------------------------------------
\begin{center}
    \begin{minipage}[b]{0.24\textwidth}
            \large +45 52 78 13 49 \\
            \large \href{mailto:zshelton1997@gmail.com}{zacharshel10@gmail.com} 
    \end{minipage}% 
    \begin{minipage}[b]{0.5\textwidth}
            \centering
            {\Huge Zach Shelton} \\ %
            \vspace{0.1cm}
            {\color{UI_blue} \Large{Data Scientist}} \\
    \end{minipage}% 
    \begin{minipage}[b]{0.24\textwidth}
            \flushright \large
            {\href{https://www.linkedin.com/in/zshelton/}{linkedin:zshelton} } \\

    \end{minipage}   
    
\vspace{-0.15cm} 
{\color{UI_blue} \hrulefill}
\end{center}

\justify
\setlength{\parindent}{0pt}
\setlength{\parskip}{12pt}
\vspace{0.1cm}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  First 2 Lines
%%%%%%% --------------------------------------------------------------------------------------

Date: \today \par \vspace{-0.1cm}

To whom it may concern,

I am writing to express my strong interest in the Digital Business Analyst position at Carlsberg Group. With my academic background and hands-on experience in academic research and data-driven startups in Denmark, I am well-prepared to contribute effectively to a team of driven and like-minded professionals. Having lived in Denmark for three years, I take great pride in the opportunity to support and collaborate with an international brand like Carlsberg.

During my studies, I collaborated with a multinational team on the Compact Muon Solenoid (CMS) Experiment at CERN, where I developed machine learning algorithms to analyze large-scale datasets. My work involved creating predictive models to isolate specific decay events from kinematics data using neural networks, decision trees, and ML libraries such as XGBoost, TensorFlow, and Keras. I also worked on large server grids at CERN and FermiLab, managed by Google Cloud services. This experience in machine learning positions me well to contribute to cutting-edge LLM and ML-based solutions.

At Wolfram Research, I taught Wolfram Language and guided university students on data-intensive projects, including financial modeling, statistical analysis, and machine learning applications. My role required quickly learning new scientific and technological fields and helping students apply data analysis to support university researchers. These projects culminated in public academic reports for the students' colleagues and Wolfram's community. I also used JIRA to manage student researcher output, implementing a less structured scrum approach. This experience honed my ability to communicate effectively with both technical and non-technical stakeholders.

Most recently, I worked as a Data Engineer at Uptimus, a Danish startup focused on last-mile delivery optimization for clients like Bring and Nemlig. I designed future data-streaming and integration solutions for an ETL pipeline, enabling the mapping of data from various vehicle makes and models to Uptimus' internal tracking system. My work involved preparing production-ready scripts using tools like Docker, Azure, PostgreSQL, GitHub, and QGIS. This role strengthened my proficiency in core Python libraries (such as pandas, NumPy, and SciPy) and enhanced my ability to thrive in a CI/CD environment with continuous data streaming from vehicles in Sjælland.

At Carlsberg, I hope to join a well-organized development environment and grow my technical skills alongside colleagues at a company with a rich history and inspiring facilities like those in Carlsberg Byen. I am happy to provide references, including my supervisor at Uptimus, who can speak to my technical abilities and work ethic. Please feel free to contact me via phone or email to discuss my application or arrange an interview.
\par
%%%
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  SIGNATURE
%%%%%%% --------------------------------------------------------------------------------------

\vspace{0.5cm}
\raggedright
Respectfully, \\ 
Zach Shelton \\ 

\end{document}
