%-------------------------
% Entry-level Cover-letter Template in LaTeX
% Made to go with "Entry-level Resume in laTeX" - here
% Version - v1.0
% Last Edits - October 5, 2021
% Author : Jayesh Sanwal
% Reach out to me on LinkedIn(/in/jsanwal), with any suggestions, ideas, issues, etc.
%------------------------
% !TEX program = xelatex

%%%% Define Document type
\documentclass[11pt,a4]{article}

%%%% Include Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
 \usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{ragged2e}
\usepackage{anyfontsize}

%%%% Set Margins
\usepackage[margin=1cm]{geometry}

%%%% Set Fonts
\setmainfont[
BoldFont=SourceSansPro-Semibold.otf,
ItalicFont=SourceSansPro-RegularIt.otf
]{SourceSansPro-Regular.otf}

%%%% Set Page Style
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color, Page Number Color, Footer Text
\definecolor{UI_blue}{RGB}{32, 64, 151}
\definecolor{HF_color}{RGB}{179, 179, 179}

%%%% Set Heading Format
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-0.7cm} \hrulefill \vspace{-0.2cm}]
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  END OF "DO NOT TOUCH" REGION
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------



\begin{document}
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  HEADER
%%%%%%% --------------------------------------------------------------------------------------
\begin{center}
    \begin{minipage}[b]{0.24\textwidth}
            \large 52 78 13 49 \\
            \large \href{mailto:zacharshel10@gmail.com}{zacharshel10@gmail.com} 
    \end{minipage}% 
    \begin{minipage}[b]{0.5\textwidth}
            \centering
            {\Huge Zach Shelton} \\ %
            \vspace{0.1cm}
            {\color{UI_blue} \Large{software Engineer}} \\
    \end{minipage}% 
    \begin{minipage}[b]{0.24\textwidth}
            \flushright \large
            {\href{https://www.linkedin.com/in/zshelton/}{linkedin.com/in/zshelton/} } \\

    \end{minipage}   
    
\vspace{-0.15cm} 
{\color{UI_blue} \hrulefill}
\end{center}

\justify
\setlength{\parindent}{0pt}
\setlength{\parskip}{12pt}
\vspace{0.1cm}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  First 2 Lines
%%%%%%% --------------------------------------------------------------------------------------

Date: \today \par \vspace{-0.1cm}

To Professor Rasmus Bjørk,

I am writing to express my strong interest in joining DTU Energy. My academic background in experimental particle physics, combined with hands-on experience at a data-driven startup in Denmark, has prepared me to contribute effectively to a team of curious, driven, and like-minded professionals. I have research and software developement experience at my previous positions and am ready to contribute at DTU.

During my studies, I collaborated with a multinational team on the Compact Muon Solenoid (CMS) Experiment at CERN, where I developed machine learning algorithms to analyze large-scale datasets. My work involved creating predictive models to isolate specific decay events from kinematics data using neural networks, decision trees, and libraries such as XGBoost, TensorFlow, and Keras. I have completed courses in electrodynamics, applied statistics(particle physics focused) and electromagnetism at BSc and MSc levels. I am ready to quickly join and contribute to the MagTense model and help improve algorithms.

In my role at Wolfram Research, I taught Wolfram Language and guided university students on data-intensive projects, including financial modeling, statistical analysis, and machine learning applications. These projects spanned diverse fields such as GIS, mathematics, physics, and chemistry, giving me the adaptability to quickly learn new domains and communicate insights. I treated the students' project in a way similar to a SCRUM attempting to maintain proper timelines and accountability. At Wolfram, I will be able to excel in a large team and quickly get up to speed with whatever tasks and roles I need to fill in support of research.

Most recently, as a Data Engineer at Uptimus, a Danish startup focused on last-mile delivery optimization, I designed ETL pipelines and data integration solutions using GIT. My work involved preparing production-ready scripts, leveraging tools like Docker, Azure, and PostgreSQL, and applying geospatial analysis with QGIS and Python libraries. With the data streamed from delivery vehicles throughout Sjælland, I am ready to quickly begin contributing to an existing codebase and help ensure good version control while improving the simulation.

At DTU, I look forward to contribute to new magnetic simulations and help improve technologies like EVs or wind turbines. I have attached references, including my supervisor at Uptimus, who can speak to my technical abilities and work ethic. Please feel free to contact me via phone or email to discuss my application or arrange an interview.

Thank you for considering my application. I am excited about the opportunity to learn and contribute at DTU!
%%%
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  SIGNATURE
%%%%%%% --------------------------------------------------------------------------------------

\vspace{0.5cm}
\raggedright
Respectfully, \\ Zach Shelton \\ +45 52 78 13 49 \\ 
\href{mailto:zshelton1997@gmail.com}{zacharshel10@gmail.com} 

\end{document}


