%-------------------------
% Entry-level Cover-letter Template in LaTeX
% Made to go with "Entry-level Resume in laTeX" - here
% Version - v1.0
% Last Edits - October 5, 2021
% Author : Jayesh Sanwal
% Reach out to me on LinkedIn(/in/jsanwal), with any suggestions, ideas, issues, etc.
%------------------------
% !TEX program = xelatex


%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  STARTING HERE, DO NOT TOUCH ANYTHING 
%%%%%%% --------------------------------------------------------------------------------------

%%%% Define Document type
\documentclass[11pt,a4]{article}

%%%% Include Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
 \usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{ragged2e}
\usepackage{anyfontsize}

%%%% Set Margins
\usepackage[margin=1cm]{geometry}

%%%% Set Fonts
\setmainfont[
BoldFont=SourceSansPro-Semibold.otf,
ItalicFont=SourceSansPro-RegularIt.otf
]{SourceSansPro-Regular.otf}

%%%% Set Page Style
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color, Page Number Color, Footer Text
\definecolor{UI_blue}{RGB}{32, 64, 151}
\definecolor{HF_color}{RGB}{179, 179, 179}

%%%% Set Heading Format
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-0.7cm} \hrulefill \vspace{-0.2cm}]
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  END OF "DO NOT TOUCH" REGION
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------



\begin{document}
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  HEADER
%%%%%%% --------------------------------------------------------------------------------------
\begin{center}
    \begin{minipage}[b]{0.24\textwidth}
            \large +45 52 78 13 49 \\
            \large \href{mailto:zacharshel10@gmail.com}{zacharshel10@gmail.com} 
    \end{minipage}% 
    \begin{minipage}[b]{0.5\textwidth}
            \centering
            {\Huge Zach Shelton} \\ %
            \vspace{0.1cm}
            {\color{UI_blue} \Large{Data Engineer | Data Scientist}} \\
    \end{minipage}% 
    \begin{minipage}[b]{0.24\textwidth}
            \flushright \large
            {\href{https://www.linkedin.com/in/zshelton/}{linkedin:zshelton} } \\
            zacharshel10@gmail.com
    \end{minipage}   
    
\vspace{-0.15cm} 
{\color{UI_blue} \hrulefill}
\end{center}

\justify
\setlength{\parindent}{0pt}
\setlength{\parskip}{12pt}
\vspace{0.1cm}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  First 2 Lines
%%%%%%% --------------------------------------------------------------------------------------

Date: \today \par \vspace{-0.1cm}

To whom it may concern,

Seaborg's molten salt reactors represent a cutting-edge advancement toward a sustainable future. I pursued studies in subatomic, nuclear, and particle physics with the goal of conducting impactful research in physics and, most importantly, making a positive contribution to society and the world. A role at Seaborg would not only be a dream come true but also the fulfillment of a promise I made to myself when I began my bachelor's degree. I am hopeful to join Seaborg as a multiphysics specialist.

During my academic career, I collaborated with a multinational team on the Compact Muon Solenoid (CMS) Experiment at CERN. As an undergraduate, I designed testing PCBs to verify the functionality of calorimeters before their installation in CMS. This work culminated in a five-year process, and the equipment I helped calibrate is still in use today. After completing my undergraduate degree, I refined my scientific programming skills by developing machine learning algorithms to analyze particle data and identify hadronic top quark decays. This was a significant challenge due to the vast volume of data, and it ultimately led me to pursue a career as a data engineer. My passion for physics, particularly subatomic physics, has driven me to continue exploring the field. Currently, I am most interested in plasma physics and nuclear physics. At Seaborg, I am eager to take on the challenge of working with molten salt reactors and contributing to both customers and colleagues.

At Wolfram Research, I taught the Wolfram Language and mentored university students on data-intensive projects, including chemistry, quantum computing, and machine learning applications. During my time at Wolfram, I refined my ability to conduct quick and thorough research on both familiar and entirely new topics. I led Master's and PhD students in writing academic-style public posts on Wolfram's Community for professionals, other academics, and enthusiasts. From editing to outlining, I sharpened my communication skills and am ready to help my colleagues with scientific writing and conference presentations.

Most recently, as a Data Engineer at Uptimus, a Danish startup specializing in last-mile delivery optimization for clients like Bring and Nemlig, I designed data-streaming and integration solutions for an ETL pipeline. In this role, I honed my practical development skills by writing and documenting production-ready Python scripts. I also utilized tools such as Docker, Azure, PostgreSQL, and GitHub while strengthening my proficiency in core data transformation libraries like pandas, NumPy, and SciPy. Whether the preferred tool or language is MatLab, Python, C++, or the Wolfram Language, I am confident in my ability to adapt and collaborate effectively at Seaborg.

I view a role at Seaborg as a career goal—an opportunity to work in Denmark, in a field I have dedicated countless nights to studying, and to contribute to making the world a better place. I can provide references, including my supervisor at Uptimus, who can speak to my technical abilities and work ethic. Please feel free to contact me via phone or email to discuss my background or to arrange an interview.
\par
%%%
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  SIGNATURE
%%%%%%% --------------------------------------------------------------------------------------

\vspace{0.5cm}
\raggedright
Respectfully, \\ 
Zach Shelton \\ 

\end{document}
