%-------------------------
% Entry-level Cover-letter Template in LaTeX
% Made to go with "Entry-level Resume in laTeX" - here
% Version - v1.0
% Last Edits - October 5, 2021
% Author : Jayesh Sanwal
% Reach out to me on LinkedIn(/in/jsanwal), with any suggestions, ideas, issues, etc.
%------------------------


%%%% Define Document type
\documentclass[11pt,a4]{article}

%%%% Include Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
 \usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{ragged2e}
\usepackage{anyfontsize}

%%%% Set Margins
\usepackage[margin=1cm]{geometry}

%%%% Set Fonts
\setmainfont[
BoldFont=SourceSansPro-Semibold.otf,
ItalicFont=SourceSansPro-RegularIt.otf
]{SourceSansPro-Regular.otf}

%%%% Set Page Style
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color, Page Number Color, Footer Text
\definecolor{UI_blue}{RGB}{32, 64, 151}
\definecolor{HF_color}{RGB}{179, 179, 179}

%%%% Set Heading Format
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-0.7cm} \hrulefill \vspace{-0.2cm}]
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  END OF "DO NOT TOUCH" REGION
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------



\begin{document}
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  HEADER
%%%%%%% --------------------------------------------------------------------------------------
\begin{center}
    \begin{minipage}[b]{0.24\textwidth}
            \large 52 78 13 49 \\
            \large \href{mailto:zshelton1997@gmail.com}{zacharshel10@gmail.com} 
    \end{minipage}% 
    \begin{minipage}[b]{0.5\textwidth}
            \centering
            {\Huge Zach Shelton} \\ %
            \vspace{0.1cm}
            {\color{UI_blue} \Large{Data Engineer} \\
    \end{minipage}% 
    \begin{minipage}[b]{0.24\textwidth}
            \flushright \large
            {\href{https://www.linkedin.com/in/zshelton/}{linkedin.com/in/zshelton/} } \\

    \end{minipage}   
    
\vspace{-0.15cm} 
{\color{UI_blue} \hrulefill}
\end{center}

\justify
\setlength{\parindent}{0pt}
\setlength{\parskip}{12pt}
\vspace{0.1cm}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  First 2 Lines
%%%%%%% --------------------------------------------------------------------------------------

Date: \today \par \vspace{-0.1cm}
%To whom it may concern, 

%I am writing to express my interest in a position at TooGoodToGo. Through my academic journey, earning both my bachelor’s and master’s degrees, I have developed a strong foundation in the theoretical and statistical principles of high-energy physics. %I joined a multi-national team at FermiLab in Chicago, where we tested and calibrated scintillating measurement devices for installation in the Compact Muon Solenoid (CMS) Experiment at CERN. 
%In my work with CMS, I applied machine learning to analyze composite particles via their decay products, focusing on identifying top quark decay from reconstructed quark jets. To tackle this, I used deep learning neural networks and machine learning methods, such as boosted decision trees and regression modeling, leveraging Python packages like XgBoost, Keras, and TensorFlow. The challenge of handling vast datasets—ranging from 100,000 to over a billion particle events—ignited my interest in data science and motivated me to deepen my technical expertise in this area.

%At Wolfram Research I guided and taught Wolfram Language to undergraduate and graduate students in researching a variety of projects, from PDE solvers to high-energy physics experiment analysis. My work has refined my data analysis methods and broadened my ability to handle diverse datasets. In Denmark, I am working with the startup Uptimus, where I contribute to developing data insights for last-mile delivery companies focused on safety and energy efficiency. Uptimus took data sources from various automotive manufacturers and ETL strategies to give last mile delivery companies data insights and cost savings. I have been able to further improve my data science skills and learn some new tools like postgreSQL, Azure and Docker.

%I am an avid user of TooGoodToGo, I find the company's mission and technology inspiring. I'd be grateful to join TooGoodToGo helping to minimize food waste and contributing to a better, greener future. Thank you for considering my application, I can provide references and recommendations if requested. 

%Please feel free to contact me via phone or email. \textbf{Feel free to consider me for any other role on at TooGoodToGo}. I look forward to the opportunity to discuss how my background and skills align with the goals of TooGoodToGo and it's clients. 


To whom it may concern

I am writing to express my strong interest in a Data Engineer position at HelloFresh. My academic background, combined with hands-on experience at a data-driven startup in Denmark, has prepared me to contribute effectively to a team of driven and like-minded professionals. HelloFresh's mission to minimize food waste and improve people's diets resonates with me.

During my studies, I collaborated with a multinational team on the Compact Muon Solenoid (CMS) Experiment at CERN, where I developed machine learning algorithms to analyze large-scale datasets. My work involved creating predictive models to isolate specific decay events from kinematics data using neural networks, decision trees, and libraries such as XGBoost, TensorFlow, and Keras. I've worked on large server grids at CERN and FermiLab in the process of my research and these servers were managed by Google Cloud services. My experience puts me in the perfect position to manage incoming data streams and quickly make analyses for colleagues and non-technical stakeholders.

In my role at Wolfram Research, I taught Wolfram Language and guided university students on data-intensive projects, including financial modeling, statistical analysis, and machine learning applications. My role would be best described as a data scientist for almost any field of study. I was tasked with quickly learning a field of science and technology and helping researchers apply methods of data analysis and visualization. All of this experience gave me the adaptability to quickly learn new domains and communicate insights effectively to both technical and non-technical stakeholders.

Most recently, I worked as a Data Engineer at Uptimus, a Danish startup focused on last-mile delivery optimization working with clients like Bring and Nemlig. I designed future data streaming and data integration solutions for Uptimus. My work involved preparing production ready scripts, leveraging tools like Docker, Azure, and PostgreSQL, Github, and applying geospatial analysis with QGIS and Python libraries. With the data streamed from delivery vehicles throughout Sjælland, I further improved my ability to think on my feet and learned more data organization methods.

At HelloFresh, I hope to join an agile development environment and grow my technical skills with colleagues motivated to create a positive workplace and a better world through healthier living. I have attached references, including my supervisor at Uptimus, who can speak to my technical abilities and work ethic. Please feel free to contact me via phone or email to discuss my application or arrange an interview.

Thank you for considering my application. I am excited to have the opportunity to contribute at Abacus.
%%%
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  SIGNATURE
%%%%%%% --------------------------------------------------------------------------------------

\vspace{0.5cm}
\raggedright
Respectfully, \\ Zach Shelton \\ \\ +45 52 78 13 49 \\ 
\href{mailto:zshelton1997@gmail.com}{zacharshel10@gmail.com} 

\end{document}
