%-------------------------
% Entry-level Cover-letter Template in LaTeX
% Made to go with "Entry-level Resume in laTeX" - here
% Version - v1.0
% Last Edits - October 5, 2021
% Author : Jayesh Sanwal
% Reach out to me on LinkedIn(/in/jsanwal), with any suggestions, ideas, issues, etc.
%------------------------
% !TEX program = xelatex

%%%% Define Document type
\documentclass[11pt,a4]{article}

%%%% Include Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
 \usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{ragged2e}
\usepackage{anyfontsize}

%%%% Set Margins
\usepackage[margin=1cm]{geometry}

%%%% Set Fonts
\setmainfont[
BoldFont=SourceSansPro-Semibold.otf,
ItalicFont=SourceSansPro-RegularIt.otf
]{SourceSansPro-Regular.otf}

%%%% Set Page Style
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color, Page Number Color, Footer Text
\definecolor{UI_blue}{RGB}{32, 64, 151}
\definecolor{HF_color}{RGB}{179, 179, 179}

%%%% Set Heading Format
\titleformat{\section}{
\color{UI_blue} \scshape \raggedright \large 
}{}{0em}{}[\vspace{-0.7cm} \hrulefill \vspace{-0.2cm}]
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  END OF "DO NOT TOUCH" REGION
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%% --------------------------------------------------------------------------------------



\begin{document}
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  HEADER
%%%%%%% --------------------------------------------------------------------------------------
\begin{center}
    \begin{minipage}[b]{0.24\textwidth}
            \large 52 78 13 49 \\
            \large \href{mailto:zshelton1997@gmail.com}{zacharshel10@gmail.com} 
    \end{minipage}% 
    \begin{minipage}[b]{0.5\textwidth}
            \centering
            {\Huge Zach Shelton} \\ %
            \vspace{0.1cm}
            {\color{UI_blue} \Large{Data Engineer}} \\
    \end{minipage}% 
    \begin{minipage}[b]{0.24\textwidth}
            \flushright \large
            {\href{https://www.linkedin.com/in/zshelton/}{linkedin.com/in/zshelton/} } \\

    \end{minipage}   
    
\vspace{-0.15cm} 
{\color{UI_blue} \hrulefill}
\end{center}

\justify
\setlength{\parindent}{0pt}
\setlength{\parskip}{12pt}
\vspace{0.1cm}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  First 2 Lines
%%%%%%% --------------------------------------------------------------------------------------

Date: \today \par \vspace{-0.1cm}
%%%

To whom it may concern,

I am writing to express my strong interest in the Data Engineer position at Tryg. My academic background, combined with hands-on experience at a data-driven startup in Denmark, has prepared me to contribute effectively to a team of curious, driven, and like-minded professionals. The opportunity to work more with cloud-based solutions and participate in a larger CI environment excites and motivates me for the position.

During my studies, I collaborated with a multinational team on the Compact Muon Solenoid (CMS) Experiment at CERN, where I developed machine learning algorithms to analyze large-scale datasets. My work involved creating predictive models to isolate specific decay events from kinematics data using neural networks, decision trees, and libraries such as XGBoost, TensorFlow, and Keras. This experience not only honed my Python skills, but also strengthened my ability to manage complex data structures, perform exploratory analysis, and uncover meaningful correlations.

In my role at Wolfram Research, I taught Wolfram Language and guided university students on data-intensive projects, including financial modeling, statistical analysis, and machine learning applications. These projects spanned diverse fields such as GIS, mathematics, physics, and chemistry, giving me the adaptability to quickly learn new domains and communicate insights effectively to both technical and non-technical stakeholders.

Most recently, as a Data Engineer at Uptimus, a Danish startup focused on last-mile delivery optimization, I designed ETL pipelines and data integration solutions. My work involved preparing production-ready scripts, leveraging tools like Docker, Azure, and PostgreSQL, and applying geospatial analysis with QGIS and Python libraries. With the data streamed from delivery vehicles throughout Sjælland, I developed a keen ability to think on my feet and continuously improve processes. Outside of my work at Uptimus, I have been exploring PowerBI and learning how to effectively work and manage data in the Microsoft ecosystem.

At Tryg, I look forward to contributing to dynamic data streaming pipelines while deepening my expertise in Python and exploring new techniques. I am currently completing my Danish classes at level PD 2.5, and I will be able to write professional emails and communications. I have attached references, including my supervisor at Uptimus, who can speak to my technical abilities and work ethic. Please feel free to contact me via phone or email to discuss my application or arrange an interview.

Thank you for considering my application. I am excited about the opportunity to contribute to Tryg’s innovative team.
%%%
%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  SIGNATURE
%%%%%%% --------------------------------------------------------------------------------------

\vspace{0.5cm}
\raggedright
Respectfully, \\ Zach Shelton 
\\ 
+45 52 78 13 49 \\ 
\href{mailto:zacharshel10@gmail.com}{zacharshel10@gmail.com} 

\end{document}
